Carbonate chemistry at Ny-Ålesund

### 2021-02-09 awipev-CO2.Rmd
added ggreg

#################### Regression function
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(xdata, ydata)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
  geom_point(size = 2, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue")  + 
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3)))
}

>>>>

#################### Regression function
# function regression plot with equation (MA or OLS) in title
ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title") { # x and y are the names of the variables
  fit_data <- tibble(xdata, ydata)
  colnames(fit_data) = c("xdata", "ydata")
  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
if (type == "OLS") ty = 1 #one selects OLS only
if (type == "MA") ty = 2 #one selects MA only
#reg <- fit$regression.results[ty,] #one selects OLS only
intercept <- fit$regression.results$Intercept[ty]
slope <- fit$regression.results$Slope[ty]
if (plot == TRUE) {
  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
  geom_abline(aes(intercept = intercept, slope = slope),
              colour = "blue")  + 
  labs(title = paste(title, "; type: ", type,
                     "\n R2 = ", round(fit$rsquare, digits = 2),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3)))
  return(plt)
  } else {
  return(fit)
}
}
